---
title: "Cabbages"
author: "Melanie Monteros!"
date: "january 31, 2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
### Plot boxplots

```{r}
boxplot(VitC~Cult,data=veggy)
```

the c39 box is completely lower then the c52 box which can tell us that it has a  significant statistical result. The boxplot shows Vitc over Cult, the data in the boxplot represents the data that was collected. c52 is in comparison to c39. The median for c52 is roughly 65 and the median for c39 is 52.
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
# Numerical results

```{r}
favstats(VitC~Cult,data=veggy)
```

The comparison between the two data analysis from the boxplot c39 and c52 shows the exact median for both and shows additional data such as height from the boxplot which is being represented in Q3 and Q1. they show statistical difference when the data point are being compared.m 
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
  
```{r}
t.test(VitC~Cult,data=veggy)
```

The data point collected is 0.00000003405 showing that it is extremely small and the difference shows that between the two groups where the data was collected c39 and c52 there is a 95% difference because they are both statistically different from each other.

# Discussion and Conclusion

We used the necessary tools in order to show the statistical differences from the data point in veggy. We used a box plot to visually represent what is happening with the data points and give a visual representation of what it is happening.
Secondly we used a numerical description in order to show numerically the
statistical differences through the comparison of the data being shown in the box plot Lastly, a T-test was run to show how statistically different the two points actually were to understand that they had a 95% difference from each other and therefore was the reason for the different data points in the boxplot and numerical data.

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
